\documentclass{article}
\textwidth 7in \addtolength{\oddsidemargin}{-2.8cm} \textheight 9in \addtolength{\topmargin}{-1in} \setlength{\parindent}{0pt} \setlength{\parskip}{0.5cm} \topskip 0.0in \everymath{\displaystyle} \pagestyle{empty}

\title{Questions: Fuzzy Logix}
\author{Rishabh Nigam(10598) }
\date{Oct 27}

\begin{document}
\maketitle
\subsection*{Q. If you were to be the president of Board of Cricket Control in India (BCCI), what would you do to preserve and promote the future on cricket in India? Keep in mind that the future of cricket will be bright only if the sport continues to attract more and more talented players and enjoys support amongst the fans.}

I believe that to ensure a bright future of cricket in India, we need to have more talented people on the ground. To ensure that, I would focus on the condition of cricket at state and lower levels. I will do the following.
\begin{itemize}
\item Allocate more budget to the state level cricket, by getting in more advertisements, more investors.
\item Introduce a tournament where our state teams get to play in foreign grounds with foreign teams. Main motive behind this is to provide international experience to state teams, which will help in producing better cricketers. 
\item Shorter matches in state level tournaments, this will help in involving more audience, and thus will help in getting more investors for the game.
\end{itemize}

Apart from this, I would also try to get the Indian pitches to be helpful for fast bowlers, thus improving the condition of Indian fast bowlers. Another thing that I would like to initiate is a better selection procedure, which is based purely on statistics, thus a player not performing well, will have to leave the team. This will help in removing the politics behind selection and also allow young players to get early exposure in the national team. Another new idea could be to introduce a policy of 2 new players every series, (apart from world cups, Asia cup and other big tournaments). If we are able to pursue this, it will give us around 30 new members to look at in an year, which will be a good place to harness young talent.


\subsection*{Q. It is 2014 and India has had general elections. Imagine that you are the next Prime Minister. What are the three most important things you will do in next 100 days and why? What lasting impact do you think those decisions will have on the country}

\textbf{Agricultural reforms.} There is an urgent need to focus on rural human capital formation and reorient our focus on the irrigation sector. I would start building a comprehensive National Rural and Agricultural Policy with the focus on augmenting agricultural production. The first few steps in this direction would be to get trends of agricultural production in the years to come and start planning according. \textbf{Benefits}- There is an urgent need to reduce influx of people to cities from rural areas. The city infrastructure cannot develop so fast to cater to both natural increase and the pressure exerted by mass migrations. The rural capital formation, decentralized cottage industries will give them the means to supplement their agricultural incomes and thus people wont be forced to grow cash crops instead of food crops and also not abandon cropping altogether. We are less than 30 years away from losing our food sufficiency. Increased yield will not only help the nation but also the 60\% of our population dependent on agricultural income. Since any research will take at least a decade, NOW is the right time to take the first leap in this direction before its too late. Something I read recently- \textbf{Once in life we need a doctor, once a lawyer, once a priest but 3 times a day everyday we need a farmer}

\textbf{Judicial reforms - need of the hour.} 
A quote about our present scenario in judicial reforms- \textbf{Progress of a civil suit in our courts of law is the closest thing to eternity we can experience!}. With the commencement of High Courts in 1990, 1.9 million cases were pending in the High Courts. In 10 years the figure has touched about 3.4 million. Half of the cases are more than 3 years old. I would initiate a more independent and impartial judiciary and start laying the foundation for a speedy and efficient judiciary system.  \textbf{Benefits-} A more independent judiciary system will be able to take decisions faster and will put all the corrupt politicians behind the bars. It will help in maintaining the peace in the country and will bring justice to allot of people who have given up hope.

\textbf{Education reforms}
The quality of education is far below where it should be in present times. This is mainly because of lack of qualified teachers. To improve this area, I would take drastic measures, increasing the salary/benefits of a teacher and organizing high competitive, year long training program for being recruited as a teacher. \textbf{Benefits-} Removing illiteracy will help us in tackling a lot of problems such as poverty, corruption, bad political choices.

\subsection*{Q. If you were to be the CEO of Fuzzy Logix today, what will be your most important decision in the next 1 year? How do you think it will impact the future of Fuzzy Logix?}

As a CEO, I would always try to make my team believe that building awesome products is the only way in which you can deliver. If you do everything, but your products are not up to the mark, then it will not give you good outcomes.

As fuzzy logix is the leading provider of advanced analytics solutions, I would like to expand in this domain and achieve a monopoly in the front of advanced analytics (For instance, I believe we could have a major impact if we take advanced analytics to the domain of advertisements. With this market growing over \$500 billion, advertisements is a fast growing section and is a potential market for data analytics(has a lot of scope on targeting the right audience).

I will also put some of the force towards marketing the company softwares to the set of possible consumers. This may involve educating small and growing startups, to the need of data analytics in their starting period. Other set of marketing could be to target big companies and get them to use our analytics on a more regular basis. The impact of this basically goes with the mission of fuzzy logix i.e \textbf{to make analytics pervasive in all walks of life.}

\end{document}